### 2019-07-02 paper_03_toy_model/article.tex

Large scale geophysical flows are often mentioned as possible applications in the context of two-dimensional (2D) turbulence whose fundamental features were first predicted in the seminal paper  by \citet{Kraichnan1967}, which this Focus Issue is commemorating.
\citet{Gage:1979} and \citet{Lilly:1983} suggested that the $ k^{-5/3} $ energy spectrum at atmospheric mesoscales, that are wave lengths from a few km up to five hundred km, measured by aircraft \citep{Nastrom-Gage:1985, Lindborg:1999}, is produced by an inverse energy cascade of similar type as described by \citet{Kraichnan1967}, a  hypothesis which recently was revived by \citet{Xia2011}. 
In the introduction of their excellent review article on 2D turbulence \citet{Boffetta2012} write that "large-scale motions in the atmosphere and oceans are described, to first approximation, as 2D turbulent fluids". There are almost countless examples of articles on 2D turbulence in which large scale geophysical flows are mentioned as possible applications. 
However, the two-dimensional Navier-Stokes equations is  a very crude model for geophysical turbulence. Fundamental features of geophysical flows such as inertia-gravity waves are absent. Moreover, the inverse energy cascade of two-dimensional turbulence is far from telling the whole story  about energy exchanges between different scales of motion in the atmosphere. In Fig.~\ref{Flux} we have reproduced  a plot from \citet{Augier-Lindborg:2013} showing spectral energy fluxes calculated in the framework of spherical harmonics, $ Y_l^m $, from a General Circulation Model (GCM) called AFES \citep{Hamilton-Takahashi-Ohfuchi:2008}.
Using these base functions the spectral energy flux can be calculated from solutions to the primitive equations \citep{Vallis:book} on a sphere as a function of wave number $ l $, after summation over wave number $ m $, in a corresponding way as the spectral energy flux can be calculated in Fourier space from solutions of Navier-Stokes equations on a plane. 
As shown by  \citet{Augier-Lindborg:2013} the flux can be calculated in a consistent way at each pressure level from a full  GCM. In the figure  we see spectral energy fluxes measured in $ W/m^2 $, integrated over all 24 levels of the model. In contrast to the case of  two-dimensional Navier-Stokes turbulence, the total spectral energy flux, $ \Pi (l) $  (black curve), of the primitive equations is the sum of the fluxes of two different forms of energy, the Kinetic Energy (KE) flux, $ \Pi_K(l) $, (red solid curve) and the flux, $ \Pi_A(l) $, of Available Potential Energy (APE) (blue curve). As shown by \citet{Lorenz:1955}, under certain approximations APE is quadratic in potential temperature and the sum of KE and APE is conserved by the primitive equations. For readers not familiar with Geophyscial Fluid Dynamics, potential temperature is the temperature a fluid element would have in case it would be adiabatically displaced to a reference pressure level. 
In Fig.~\ref{Flux}, the fast increase of $ \Pi_A $  at  $ l \in [1, 3] $ means that  APE is forced at planetary scales of motions. The decrease of $ \Pi_A $ at $ l \in [8, 30] $ is matched by a corresponding increase of $ \Pi_K $. In this wave number range APE is converted into KE by baroclinic instability \citep{Vallis:book} which is the mechanism producing large scale weather systems.  The green curve, $ C_{cum}(l) $,  is the cumulative spectral conversion from APE to KE. A decrease of $ C_{cum}(l) $ in a certain wave number range corresponds to the amount of energy which is converted from APE to KE in that range.

>>>>

Large scale geophysical flows are often mentioned as possible applications in the context of two-dimensional (2D) turbulence whose fundamental features were first predicted in the seminal paper  by \citet{Kraichnan1967}, which this Focus Issue is commemorating.
\citet{Gage:1979} and \citet{Lilly:1983} suggested that the $ k^{-5/3} $ energy spectrum at atmospheric mesoscales, that are wave lengths from a few km up to five hundred km, measured by aircraft \citep{Nastrom-Gage:1985, Lindborg1999}, is produced by an inverse energy cascade of similar type as described by \citet{Kraichnan1967}, a  hypothesis which recently was revived by \citet{Xia2011}. 
In the introduction of their excellent review article on 2D turbulence \citet{Boffetta2012} write that "large-scale motions in the atmosphere and oceans are described, to first approximation, as 2D turbulent fluids". There are almost countless examples of articles on 2D turbulence in which large scale geophysical flows are mentioned as possible applications. 
However, the two-dimensional Navier-Stokes equations is  a very crude model for geophysical turbulence. Fundamental features of geophysical flows such as inertia-gravity waves are absent. Moreover, the inverse energy cascade of two-dimensional turbulence is far from telling the whole story  about energy exchanges between different scales of motion in the atmosphere. In Fig.~\ref{Flux} we have reproduced  a plot from \citet{Augier-Lindborg:2013} showing spectral energy fluxes calculated in the framework of spherical harmonics, $ Y_l^m $, from a General Circulation Model (GCM) called AFES \citep{Hamilton-Takahashi-Ohfuchi:2008}.
Using these base functions the spectral energy flux can be calculated from solutions to the primitive equations \citep{Vallis:book} on a sphere as a function of wave number $ l $, after summation over wave number $ m $, in a corresponding way as the spectral energy flux can be calculated in Fourier space from solutions of Navier-Stokes equations on a plane. 
As shown by  \citet{Augier-Lindborg:2013} the flux can be calculated in a consistent way at each pressure level from a full  GCM. In the figure  we see spectral energy fluxes measured in $ W/m^2 $, integrated over all 24 levels of the model. In contrast to the case of  two-dimensional Navier-Stokes turbulence, the total spectral energy flux, $ \Pi (l) $  (black curve), of the primitive equations is the sum of the fluxes of two different forms of energy, the Kinetic Energy (KE) flux, $ \Pi_K(l) $, (red solid curve) and the flux, $ \Pi_A(l) $, of Available Potential Energy (APE) (blue curve). As shown by \citet{Lorenz:1955}, under certain approximations APE is quadratic in potential temperature and the sum of KE and APE is conserved by the primitive equations. For readers not familiar with Geophyscial Fluid Dynamics, potential temperature is the temperature a fluid element would have in case it would be adiabatically displaced to a reference pressure level. 
In Fig.~\ref{Flux}, the fast increase of $ \Pi_A $  at  $ l \in [1, 3] $ means that  APE is forced at planetary scales of motions. The decrease of $ \Pi_A $ at $ l \in [8, 30] $ is matched by a corresponding increase of $ \Pi_K $. In this wave number range APE is converted into KE by baroclinic instability \citep{Vallis:book} which is the mechanism producing large scale weather systems.  The green curve, $ C_{cum}(l) $,  is the cumulative spectral conversion from APE to KE. A decrease of $ C_{cum}(l) $ in a certain wave number range corresponds to the amount of energy which is converted from APE to KE in that range.
